---
title: "Homework1"
author: "Ditian Li"
date: "2018/9/20"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```

# Problem 1
## Create a data frame
```{r #Problem 1-1}
set.seed(666)
p1_df = tibble(
  z = runif(10, min = 0, max = 5),
  vec_logical = z > 2,
  vec_char = c("a", "b", "c", "d","e","f","g","h","i","j"),
  vec_factor = factor(c("male", "male", "female", "female","male", "male", "female", "female", "female", "female"))
)

```

## Mean
```{r #Problem 1-2}

mean(p1_df$z)
mean(p1_df$vec_logical)
mean(p1_df$vec_char)
mean(p1_df$vec_factor)
```
Mean of the random sample of size 10 from uniform distribution and vec_logical worked, others didn't work, because they are not numeric or logical variable.

## Convert
```{r #Problem 1-3-1, result = "hide"}
as.numeric(p1_df$vec_logical)
as.numeric(p1_df$vec_char )
as.numeric(p1_df$vec_factor)
```
Character vector can't convert in to numeric vector, others could work.

```{r #Problem 1-3-2}
as.numeric(as.factor(p1_df$vec_char))
as.numeric(as.character(p1_df$vec_factor))
```
Character variable from variable to factor to variable can work, and factor variable from factor to character to numeric doesn't work.

## Problem 2
## Create data frame
```{r #Problem 2}
set.seed(999)

x = rnorm(1000)
y = rnorm(1000)
l = x + y > 0
m = as.numeric(l)
n = as.factor(m)

p2_df = tibble(x,y,l,m,n)

```

# Description
The size of the dataset `r ncol(p2_df) ` by `r nrow(p2_df) ` table.
The mean of x is `r mean(x)`.
The median of x is `r median(x)`.
The proportion of cases for which the logical vector is TRUE: `r (sum(p2_df$m)/1000)*100`%.

# Scatter plot
```{r yx_scatter1}
image1 = ggplot(p2_df, aes(x = x, y = y,color = l)) + geom_point()
ggsave("image1.png",plot = image1)
image1
```

```{r yx_scatter2}
image2 = ggplot(p2_df, aes(x = x,y = y,color = m)) + geom_point()
ggsave("image2.png",plot = image2)
image2
```

```{r yx_scatter3}
image3 = ggplot(p2_df, aes(x = x,y = y,color = n)) + geom_point()
ggsave("image3.png",plot = image3)
image3
```